Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Platoons on Air Highways

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/high_waypoints.tex
updated final submission to better match published version

There are many different ways to sparsify the close-spaced set of points on each path, and this process will not be our focus. However, for illustrative purposes, we show how this process may be started. We begin by noting the path's heading at the destination point. We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.

If there is a large change in heading within a small section of the cost-minimizing path, then the collection of points may contain many points which are close together. In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints. One way to sparsify the waypoints is to cluster the points. Afterwards, each cluster of points can be replaced by a single point located at the centroid of the cluster.

>>>>

There are many different ways to do this, and this process will not be our focus. However, for illustrative purposes, we show how this process may be started. We begin by noting the path's heading at the destination point. We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.

If there is a large change in heading within a small section of the cost-minimizing path, then the collection of points may contain many points which are close together. In addition, there may be multiple paths that are very close to each other (in fact, this behavior is desirable), which may contribute to cluttering the airspace with too many waypoints. To reduce clutter, one could cluster the points. Afterwards, each cluster of points can be replaced by a single point located at the centroid of the cluster.

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/introduction.tex
updated final submission to better match published version

% !TEX root = main.tex
\section{Introduction}
Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91}; however, recently there has been an immense surge of interest in using UAVs for civil applications. Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}. In the future, the use of UAVs is likely to become more and more prevalent.

>>>>

% !TEX root = main.tex
\section{Introduction}
Unmanned aerial vehicles (UAVs) have in the past been mainly used for military operations \cite{Tice91, Haulman2003}; however, recently there has been an immense surge of interest in using UAVs for civil applications. Through projects such as Amazon Prime Air \cite{PrimeAir} and Google Project Wing \cite{ProjectWing}, companies are looking to send UAVs into the airspace to not only deliver commercial packages, but also for important tasks such as aerial surveillance, emergency supply delivery, videography, and search and rescue \cite{Kopardekar16}. In the future, the use of UAVs is likely to become more and more prevalent.

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/main.tex
updated final submission to better match published version

\author{Mo Chen\thanks{PhD Candidate, Department of Electrical Engineering and Computer Sciences}, Qie Hu\thanksibid{1}, Jaime F. Fisac\thanksibid{1}, Kene Akametalu\thanksibid{1}, Casey Mackin\thanks{PhD Student, Department of Electrical Engineering and Computer Sciences}, Claire J. Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences}\\\textit{University of California, Berkeley}}
\title{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}

>>>>

\author{Mo Chen\thanks{PhD Candidate, Department of Electrical Engineering and Computer Sciences}, Qie Hu\thanksibid{1}, Jaime F. Fisac\thanksibid{1}, Kene Akametalu\thanksibid{1}, Casey Mackin\thanks{PhD Student, Department of Electrical Engineering and Computer Sciences}, Claire J. Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences, Member AIAA}\\\textit{University of California, Berkeley}}
\title{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Platoons on Air Highways}

### 2017-01-31 docs/AIAA 2016 highway platooning final submission/plat_safety.tex
updated final submission to better match published version

With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get near the safety BRS with respect to $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$. In this case, a ``safety breach" occurs. Our synthesis of the safety controller guarantees that between every pair of vehicles $\veh{i},\veh{k}$, as long as $V_S(-t,x_i- x_k)>0$, $\exists u_i$ to keep $\veh{i}$ from colliding with $\veh{k}$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $\veh{k}$. Therefore, as long as the number of ``safety breaches" is at most one for $\veh{i}$, $Q_i$ can simply use the optimal control to avoid $\veh{k}$ and avoid collision for the time horizon of $t$. Under the assumption that vehicles are able to exit the current altitude range within a duration of $\td$, if we choose $t=\td$, the safety breach would always end before any collision can occur.

>>>>

With our choice of $\vehSCS{i}$ and the assumption that the platoon is in a single-file formation, some vehicle $\veh{i}$ would get near the safety BRS with respect to $\veh{k}$, where $\veh{k}$ is likely to be the vehicle in front or behind of $\veh{i}$. In this case, a ``safety breach" occurs. Our synthesis of the safety controller guarantees the following: between every pair of vehicles $\veh{i},\veh{k}$, if $V_S(-t,x_i- x_k)>0$, then $\exists u_i$ to keep $\veh{i}$ from colliding with $\veh{k}$ for a desired time horizon $t$, despite the worst case (an adversarial) control from $\veh{k}$. Therefore, as long as the number of ``safety breaches" is at most one for $\veh{i}$, $Q_i$ can simply use the optimal control to avoid $\veh{k}$ and avoid collision for the time horizon of $t$. Under the assumption that vehicles are able to exit the current altitude range within a duration of $\td$, if we choose $t=\td$, the safety breach would always end before any collision can occur.
